Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-04-22 ms.tex
Adding constrained transport MHD file and call from ms.tex
fixed up some subsections.  added a subsection in 2 and 3 for thermal conductivity.
Combining MUSCL and Dedner MHD
Intermediate checkin
Revised abstract.

% Paper Outline  (last updated January 18, 2013)
%
% 1.  Introduction
% 2.  Physical equations and overview
%   2.1 Physical equations
%   2.2 Overview of numerical methods
% 3.  Numerical methods
%   3.1 AMR
%   3.2. Hydro: Godunov (PPM)
%   3.3  Hydro: Godunov (MUSCL)
%   3.4. Hydro: Finite difference (ZEUS)
%   3.5. MHD: Dedner
%   3.6. Gravity
%   3.7. Particle Integration
%   3.8. Chemistry
%   3.9. Cooling
%   3.10. Radiation: Homogeneous
%   3.11  Radiation: ray-tracing
 %  3.12  Radiation: FLD
%   3.13. Star formation & Feedback
%   3.14. Timestep constraints
% 4. Code tests
%   4.1 Verifying and Validating the Enzo code
%   4.2 Representative test problems
% 5. Parallelism 
%   5.1. Parallel strategy 
%   5.2. Parallel performance 
% 6. Code development methodology
% 7. Conclusions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{abstract}
We describe the \enzo\ code, which uses a structured adaptive mesh refinement technique to provide high spatial and temporal resolution for modeling astrophysical flows.  The code includes support for the following physics: multi-dimensional hydrodynamics, self-gravity, N-body dynamics, primordial gas chemistry, optically-thin radiative cooling, and cosmological expansion.  Two Eulerian hydrodynamic solvers are provided.  This paper describes the method as well as the code's performance on a wide range of test problems.
\end{abstract}

@@

\input{numerical-amr}
\input{numerical-ppm}
\input{numerical-muscl} % new
\input{numerical-zeus}
\input{numerical-mhd-dedner} % new
\input{numerical-gravity}
\input{numerical-particle}
\input{numerical-chemistry}
\input{numerical-cooling} % new
\input{numerical-radiation-homogeneous} % new
\input{numerical-radiation-raytracing} % new
\input{numerical-radiation-fld} % new
\input{numerical-starformation}
\input{numerical-timestep}
\input{numerical-analysis} % new

@@

>>>>

% Paper Outline  (last updated January 18, 2013)
%
% 1.  Introduction
% 2.  Physical equations and overview
%   2.1 Physical equations
%   2.2 Overview of numerical methods
% 3.  Numerical methods
%   3.1   AMR
%   3.2.  Hydro: Godunov (PPM)
%   3.3   Hydro: Godunov (MUSCL)
%   3.4   Hydro: Finite difference (ZEUS)
%   3.5   MHD: Dedner
%   3.6   MHD: CT
%   3.7   Gravity
%   3.8   Particle Integration
%   3.9.  Chemistry
%   3.10 Cooling
%   3.11 Radiation: Homogeneous
%   3.12 Radiation: ray-tracing
%   3.13 Radiation: FLD
%   3.14 Thermal conduction
%   3.15 Star formation & Feedback
%   3.16 Timestep constraints
%   3.17 Analysis
% 4. Code tests
%   4.1 Verifying and Validating the Enzo code
%   4.2 Representative test problems
% 5. Parallelism 
%   5.1 Parallel strategy 
%   5.2 Parallel performance 
% 6. Code development methodology
% 7. Conclusions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{abstract}
This paper describes the open-source \enzo\ code, which uses a
block-structured adaptive mesh refinement to provide high spatial and
temporal resolution for modeling astrophysical fluid flows.  The code
is Cartesian and can be run in 1, 2, and 3 dimensions, and supports a
large variety of physics, including hydrodynamics, ideal and non-ideal
magnetohydrodynamics, N-body dynamics (and, more broadly, self-gravity
of fluids and particles), primordial gas chemistry, optically-thin
radiative cooling of primordial and metal-enriched plasmas, radiation
transport, and cosmological expansion.  In addition to explaining the
algorithms implemented, we present solutions for a wide range of test
problems, demonstrate the code's parallel scaling properties, and
discuss the \enzo\ consortium's code development methodology.
\end{abstract}

@@

\input{numerical-amr}
\input{numerical-ppm}
\input{numerical-muscl} % new
%\input{numerical-mhd-dedner} % new (combined with muscl)
\input{numerical-mhd-ct}  % new
\input{numerical-zeus}
\input{numerical-gravity}
\input{numerical-particle}
\input{numerical-chemistry}
\input{numerical-cooling} % new
\input{numerical-radiation-homogeneous} % new
\input{numerical-radiation-raytracing} % new
\input{numerical-radiation-fld} % new
\input{numerical-conduction} % new
\input{numerical-starformation}
\input{numerical-timestep}
\input{numerical-analysis} % new

@@

\input{appendix}  % new
